SparseIDS: Learning Packet Sampling with Reinforcement Learning

### 2020-02-11 paper_rl/paper.tex
Fix pluralization

In general, we think that \gls{rl}-based packet sampling is not only applicable to \gls{ids} but we are confident that other domains of networking can benefit from similar solutions to save computational expenses.

>>>>

In general, we think that \gls{rl}-based packet sampling is not only applicable to \glspl{ids} but we are confident that other domains of networking can benefit from similar solutions to save computational expenses.
